---
title: "Linear Regression Model of using sharebikes in London"
author: "Jan Dudzik"
date: "26 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
london_merged <- read_csv("london_merged.csv")
```

## Theoretical model

Theoretical model of linear regression estimating number of bike rents in a hour takes form:
\[
y_i = \beta_0 + \beta_1*x_{i1} + \epsilon_i
\]

## Creating dependent variables

let x1 be a vector of x1i for i=1,.., N that are mean of hours feel temperatures in London
\n let beta0 be a vector of 1's representing presence of intercept 
\n let X be a matrix of observations

```{r fig.align='center', out.width = "50%"}

x1 <- as.numeric(as.character(london_merged$t2)) #temperature feels

beta0 = rep(1,times=length(x1)) #creating column of 1's 

X=cbind(beta0,x1)

```

Now let Y be vector of values of y_i, that are numbers of rented bicycles

```{r fig.align='center', out.width = "50%"}

Y = as.numeric(as.character(london_merged$cnt))


```

Using equation $\mathbf{b} = \left(  X^\top X  \right)^{-1}X^\top {y}$. let's calculate b_0 and b_1

```{r fig.align='center', out.width = "50%"}

b=solve(t(X)%*%X)%*%t(X)%*%cbind(Y)

print(b)
```
